site_map

### 2020-07-13 site_map.Rmd
update

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  #site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
  site_pixel <- transect.pixel(site, c(0, 25000, 50000))
  site_pixels <- rbind(site_pixels, site_pixel)
}

@@

# Define plotting parameters
sa_lats <- c(-37, -27); sa_lons <- c(14, 25)

>>>>

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  #site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
  site_pixel <- transect.pixel(site, c(10000, 25000, 50000))
  site_pixels <- rbind(site_pixels, site_pixel)
}

@@

write.csv(site_list_sub,file = "site_list_sub.csv")
# Define plotting parameters
sa_lats <- c(-37, -27); sa_lons <- c(14, 25)
